DOpElib:\\ Differential Equations and Optimization Environment

### 2014-10-14 Examples/description.tex
Updated DOpE to have the timestepsize hidden in the optproblemcontainer; New ControlVectorType::stationary for controls that are independent of time, but act at all timesteps.
Added support for time dependent controls and included OPT/InstatPDE/Example3 to show how to use it. Further more, a bug in the functional evaluation has been fixed, up to now it was always assumed that the type ist timelocal. This is now fixed

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title{DOpElib:\\ 
Differential Equations and Optimization Environment}
\author{
  Christian Goll\thanks{Heidelberg University, 
    {christian.goll@iwr.uni-heidelberg.de}}, 
  Thomas Wick\thanks{The University of Texas at Austin, 
    {twick@ices.utexas.edu}}, 
  Winnifried Wollner\thanks{University of Hamburg, 
    {winnifried.wollner@math.uni-hamburg.de}}
}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title{DOpElib:\\ 
Differential Equations and Optimization Environment}
\author{
  Christian Goll\thanks{Heidelberg University, 
    {christian.goll@iwr.uni-heidelberg.de}}, 
  Thomas Wick\thanks{Johann Radon Institute for Computational and Applied Mathematics (RICAM), 
    {thomas.wick@ricam.oeaw.ac.at}}, 
  Winnifried Wollner\thanks{University of Hamburg, 
    {winnifried.wollner@uni-hamburg.de}}
}

@@

\subsection{Control of the heat equation via a space dependent right hand side}
\label{OPT_Instat stationary control}
\input{OPT/InstatPDE/Example2/content.tex}
\subsection{Control of the heat equation via a time dependent right hand side}
\label{OPT_Instat nonstationary control}
\input{OPT/InstatPDE/Example3/content.tex}
